---
title: "ST 558, Homework 1"
author: "Matthew Corne"
format: html
editor: visual
---

## Part 1

### What do you think being a data scientist is about?

Being a data scientist involves working with raw data or cleaned data in different environments.  These environments include consoles, virtual desktops, and databases.

Data scientists must manipulate data as needed.  They subset the data, building smaller dataframes with only those variables of interest to themselves or customers.  They also create new variables based on the variables native to the dataframes they are investigating.

Data summary represents an important aspect of data science.  Using measures of central tendency, spread, and skewness, data scientists provide insights about the data.  Beyond this, they model data - identify distributions and assess significance - to make inference or predict outcomes within a certain confidence level.

Finally, data scientists communicate their findings using spreadsheets, plots, simulations, dashboards, and narratives.  These are similar to the work of other scientists, and in fact many scientists trained in other STEM disciplines become data scientists.

### What differences/similarities do you see between data scientists and statisticians?

Data scientists and statisticians both

* need a keen understanding of the data
* must be able to present their findings coherently and cohesively

Data scientists and statisticians differ in several ways.  First, data scientists may spend most of their time cleaning and manipulating data (e.g., merging data sets) but not necessarily looking for trends or patterns.  Statisticians look for trends and patterns in data and also develop methodologies and statistics to analyze the data.

Second, data scientists tend to use various techniques when they have to analyze the data.  Statisticians use and develop techniques for data analysis, as well as participate in experimental and survey design to collect data.

This is not to say that data scientists and statisticians do not intersect in their duties, but there are clear differences in training and background of the two occupations.

### How do you view yourself in relation to these two areas?

My job title is "mathematical statistician."  My work actually does not involve very much statistics - at most, we use basic linear regression - and in fact it doesn't involve any complicated mathematics.  My own background is in mathematics and physics, so I would say that I have more in common with statisticians except that I have never developed a survey, done statistically rigorous experimental design, or worked in frame management.  By now, my experiences with data and data manipulation probably align moreso with those of a data scientist.

## Part 2

### R Programming Code Chunk Exercises

Apply the density function to the petal width column of the iris data frame:
```{r}
y <- density(iris$Petal.Width)
```

Determine the class, type, and structure of the object y:

```{r}
class(y)
typeof(y)
str(y)
```

Use the plot function on the object y:

```{r}
#| echo: false
plot(y)
```

